---
title: "Salad Bar Study: Jepson Fruit and Vegetable Paper"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
header-includes:
- \usepackage{fullpage}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{float}
- \usepackage{placeins}
- \usepackage{caption}
- \usepackage{mathtools}
# - \usepackage{multirow}
- \usepackage{amssymb}
- \usepackage{amsmath}
- \usepackage{bigstrut}
- \usepackage{geometry}
# - \usepackage{pdflscape}
- \setlength{\parskip}{1em}
geometry: margin=1.3cm
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(comment = FALSE), echo = TRUE, fig.width=6, fig.height=4, fig.path='figs/', fig.pos='H', echo=FALSE, cache = FALSE, warning=FALSE, message=FALSE, comment = NA)
```

<!-- load startup file and any extra packages -->
```{r load, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(stats)
library(haven)
library(psycho)
library(reshape2)
library(gtsummary)
theme_gtsummary_compact()

library(car)
library(emmeans)

library(lme4)
library(lmerTest)
library(rwa)
library(ggplot2)
library(ggpubr)
library(ggsignif)


source('functions.R')
```

```{r load_scripts, echo=FALSE, results='asis'}
source('setup.R')
source('jepson_tables.R')
source('jepson_analyses.R')
source('jepson_figures.R')
```

\clearpage

# Demographic Characteristics

```{r demo_tab, echo=FALSE, results='asis'}
  as_kable_extra(partab_merge, caption = 'Demographic Characteristics', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage

## income
```{r demo_gender, echo=FALSE}
gender_chi
```

## age
```{r demo_age, echo=FALSE}
age_ttest
```

## grade
```{r demo_grade, echo=FALSE}
grade_ttest
```

## race
```{r demo_race, echo=FALSE}
race_chi
```

## ethnicity
```{r demo_ethnicity, echo=FALSE}
ethnicity_chi
```

## free-reduced lunch
```{r demo_frl, echo=FALSE}
frl_chi
```

## fruit/veg selected
```{r demo_fv_select, echo=FALSE}
fv_selected_chi
```

# Fruit/Vegetable Intake Table

```{r fv_tab, echo=FALSE, results='asis'}
  as_kable_extra(fvtab_merge, caption = 'Fruit/Vegetable Intake - for those that took only', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage

## fruit/veg amount selected
```{r demo_fv_g_select, echo=FALSE}
fv_pre_ttest
```

## fruit/veg consumed
```{r demo_fv_consumed, echo=FALSE}
fv_consumed_ttest
```

## fruit/veg waste
```{r demo_fv_waste, echo=FALSE}
fv_post_ttest
```

## fruit/veg waste proportion
```{r demo_fv_prop_waste, echo=FALSE}
fv_post_prop_ttest
```

# Fruit/Vegetable Self-Served

```{r fv_pre_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
hist(salad_bar_dat[salad_bar_dat[['fv_selected']] == 'Y' & salad_bar_dat[['fv_exclude']] == 'N', 'fv_pre'])
```

\FloatBarrier

```{r fv_pre_mod, echo=FALSE, results='asis'}
kable(round(gng_fa_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

## Fruit/Vegetable Consumed

```{r fv_consumed_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
hist(salad_bar_dat[salad_bar_dat[['fv_selected']] == 'Y' & salad_bar_dat[['fv_exclude']] == 'N', 'fv_consumed'])
```

\FloatBarrier

## Fruit/Vegetable Waste

```{r fv_waste_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
hist(salad_bar_dat[salad_bar_dat[['fv_selected']] == 'Y' & salad_bar_dat[['fv_exclude']] == 'N', 'fv_post'])
```

\FloatBarrier

\FloatBarrier


\FloatBarrier
\clearpage

### Percent Hits

```{r gng_hits_risk_mod, echo=FALSE, results='asis'}
kable(round(gng_hits_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Percent Hits', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### Go Reaction Time

```{r gng_hits_rt_mod, echo=FALSE, results='asis'}
kable(round(gng_rt_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Go Reaction Time', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### d'

```{r gng_dprime_risk_mod, echo=FALSE, results='asis'}
kable(round(gng_dprime_sum$coefficients, digits = 3), "latex",  digits = 3, caption = "Go-NoGo - d'", booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier
\clearpage

## Stop-Signal Task

```{r sst_tab, echo=FALSE, results='asis'}
as_kable_extra(sst_all_tab, caption = 'Stop-Signal Task Performance Summary: Risk Status across all trials', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```
\
\FloatBarrier


```{r sstED_tab, echo=FALSE, results='asis'}
as_kable_extra(sstED_tab, caption = 'Stop-Signal Task Performance Summary: Risk Status by Energy Density Condition', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```
\
\FloatBarrier

```{r sstPS_tab, echo=FALSE, results='asis'}
as_kable_extra(sstPS_tab, caption = 'Stop-Signal Task Performance Summary: Risk Status by Portion Size Condition', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\
\FloatBarrier
\clearpage

### Stop Signal Reaction Time

#### Design

\FloatBarrier

```{r sst_ssrtdesign_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrtdesign_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtdesign_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtdesign_plot
```


\clearpage

#### Overall

\FloatBarrier

```{r sst_ssrt_risk_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrt_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrt_plot
```


```{r sst_ssrt_risk_mod_posthoc}
emmeans(sst_ssrt_model, specs = pairwise ~ risk_status_mom)
test(emtrends(sst_ssrt_model, ~age_yr, var = 'age_yr'))
```

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier

```{r sst_ssrt_risk_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED x Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtED_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtED_plot
```


```{r sst_ssrt_risk_EDmod_posthoc}
emmeans(sst_ssrt_EDmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssrt_EDmodel, specs = pairwise ~ ED)

```
\FloatBarrier
\clearpage

#### Portion Size Trials

\FloatBarrier

```{r sst_ssrt_risk_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - PS x Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtPS_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtPS_plot
```


```{r sst_ssrt_risk_PSmod_posthoc}
emmeans(sst_ssrt_PSmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssrt_PSmodel, specs = pairwise ~ PS)

```
\FloatBarrier
\clearpage

### Stop Signal Delay

#### Design

\FloatBarrier

```{r sst_ssddesign_mod, echo=FALSE, results='asis'}
kable(round(sst_ssddesign_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - ED x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssddesign_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssddesign_plot
```


```{r sst_ssddesign_mod_posthoc, echo=FALSE}
emmeans(sstdesign_ssd_model, specs = pairwise ~ ED)
```


\FloatBarrier

```{r sst_ssddesignED_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssddesignED_plot
```

\FloatBarrier
\clearpage

#### All Trials


```{r sst_ssd_risk_mod, echo=FALSE, results='asis'}
kable(round(sst_ssd_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssd_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssd_plot
```


```{r sst_ssd_risk_mod_posthoc, echo=FALSE}
emmeans(sst_ssd_model, specs = pairwise ~ risk_status_mom)
```

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier

```{r sst_ssd_risk_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status x ED', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssdED_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssdED_plot
```


```{r sst_ssd_risk_EDmod_posthoc, echo=FALSE}
emmeans(sst_ssd_EDmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssd_EDmodel, specs = pairwise ~ ED)
```

\FloatBarrier
\clearpage

#### Portion Size Trials

\FloatBarrier

```{r sst_ssd_risk_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssdPS_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssdPS_plot
```


```{r sst_ssd_risk_PSmod_posthoc, echo=FALSE}
emmeans(sst_ssd_PSmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssd_PSmodel, specs = pairwise ~ PS)
emmeans(sst_ssd_PSmodel, specs = pairwise ~ sex)
```

\FloatBarrier
\clearpage

## N-back

```{r nback_risk_tab, echo=FALSE, results='asis'}
as_kable_extra(nbacktab_all, caption = 'Nback Performance Summary',  format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```
\
\FloatBarrier
\clearpage

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_risk_mod, echo=FALSE, results='asis'}
kable(round(nback_balacc_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

```{r nback_balacc_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
nback_balacc_plot
```


```{r nback_balacc_risk_mod_posthoc, echo=FALSE}
emmeans(nback_balacc_mod, specs = pairwise ~ block, adjust = 'none')
emmeans(nback_balacc_mod, specs = pairwise ~ risk_status_mom, adjust = 'none')

emmeans(nback_balacc_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'none')
```

\FloatBarrier
\clearpage

### d'

\FloatBarrier

```{r nback_dprime_risk_mod, echo=FALSE, results='asis'}
kable(round(nback_dprime_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

```{r nback_dprime_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
nback_drime_plot
```


```{r nback_dprime_risk_mod_posthoc, echo=FALSE}
emmeans(nback_dprime_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'none')
emmeans(nback_dprime_mod, specs = pairwise ~ block, adjust = 'none')
```

\FloatBarrier
\clearpage

# Effect of Total Body Fat Percentage

## Go-NoGo

### Percent False Alarms

\FloatBarrier

```{r gng_fa_bfp_mod, echo=FALSE, results='asis'}
kable(round(gng_fa_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\

```{r gng_fa_bfp_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
gng_fa_bfp_plot
```

\FloatBarrier

\FloatBarrier

### Percent Hits

```{r gng_hits_bfp_mod, echo=FALSE, results='asis'}
kable(round(gng_hits_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Percent Hits - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### Go Reaction Time

```{r gng_hits_rt_bfp_mod, echo=FALSE, results='asis'}
kable(round(gng_rt_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Go Reaction Time', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### d'

```{r gng_dprime_bfp_mod, echo=FALSE, results='asis'}
kable(round(gng_dprime_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = "Go-NoGo - d'", booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier
\clearpage

## Stop-Signal Task

### Stop Signal Reaction Time


#### Overall

\FloatBarrier

```{r sst_ssrt_bfp_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\

```{r sst_ssrt_bfp_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
sst_ssrt_bfp_plot
```

\FloatBarrier

### Energy Density Trials

\FloatBarrier

```{r sst_ssrt_bfp_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED x Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r sst_ssrt_bfp_EDmod_posthoc, echo=FALSE}
test(emtrends(sst_ssrt_bfp_EDmod, ~ bfp_center, var = 'bfp_center'))
emmeans(sst_ssrt_bfp_EDmod, specs = pairwise ~ ED)
```

\FloatBarrier

### Portion Size Trials

\FloatBarrier

```{r sst_ssrt_bfp_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - PS x Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r sst_ssrt_bfp_PSmod_posthoc, echo=FALSE}
test(emtrends(sst_ssrt_bfp_PSmod, ~ bfp_center, var = 'bfp_center'))
emmeans(sst_ssrt_bfp_PSmod, specs = pairwise ~ PS)
```
\FloatBarrier
\clearpage

### Stop Signal Delay

#### Overall

\FloatBarrier

```{r sst_ssd_bfp_mod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssd_bfp_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssd_bfp_plot
```


\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier
\clearpage

```{r sst_ssd_bfp_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage x ED', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r sst_ssd_bfp_EDmod_posthoc, echo=FALSE}
test(emtrends(sst_ssd_bfp_EDmod, ~ bfp_center, var = 'bfp_center'))
emmeans(sst_ssd_bfp_EDmod, specs = pairwise ~ ED)
```
\FloatBarrier
\clearpage

#### Portion Size Trials

\FloatBarrier

```{r sst_ssd_bfp_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r sst_ssd_bfp_PSmod_posthoc, echo=FALSE}
test(emtrends(sst_ssd_bfp_PSmod, ~ bfp_center, var = 'bfp_center'))
emmeans(sst_ssd_bfp_PSmod, specs = pairwise ~ PS)
```

\FloatBarrier
\clearpage

## N-back

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_bfp_mod, echo=FALSE, results='asis'}
kable(round(nback_balacc_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

```{r nback_balacc_bfp_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
nback_balacc_bfp_plot
```

```{r nback_balacc_bfp_mod_posthoc, echo=FALSE}
emmeans(nback_balacc_bfp_mod, specs = pairwise ~ block)
test(emtrends(nback_balacc_bfp_mod, ~ block:bfp_center, var = 'bfp_center'))
```

\FloatBarrier
\clearpage

### d'

\FloatBarrier

```{r nback_dprime_bfp_mod, echo=FALSE, results='asis'}
kable(round(nback_dprime_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\

```{r nback_dprime_bfp_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
nback_dprime_bfp_plot
```

\FloatBarrier
\
```{r nback_dprime_bfp_mod_posthoc, echo=FALSE}
emmeans(nback_dprime_bfp_mod, specs = pairwise ~ block)
test(emtrends(nback_dprime_bfp_mod, ~ bfp_center, var = 'bfp_center'))
```
\FloatBarrier
\clearpage

# Exploratory Analyses: relative impact of risk and body fat percentage

## Go-NoGo

### Percent False Alarms

\FloatBarrier

```{r gng_fa_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(gng_fa_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms - Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

```{r gng_fa_rwa_mod, echo=FALSE, results='asis'}
kable(gng_fa_rwa$result, "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms - Relative Weighting Analysis', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier
\clearpage

## Stop-Signal Task

### Stop Signal Reaction Time


#### Overall

\FloatBarrier

```{r sst_ssrt_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

```{r sst_ssrt_rwa_mod, echo=FALSE, results='asis'}
kable(sst_ssrt_rwa$result, "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Relative Weighting Analysis', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

### Energy Density Trials

\FloatBarrier

```{r sst_ssrt_bfp_risk_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_risk_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED  + Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

### Portion Size Trials

\FloatBarrier

```{r sst_ssrt_bfp_risk_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_risk_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - PS + Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

### Stop Signal Delay

#### Overall

\FloatBarrier

```{r sst_ssd_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

```{r sst_ssd_rwa_mod, echo=FALSE, results='asis'}
kable(sst_ssd_rwa$result, "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Relative Weighting Analysis', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier
\clearpage

```{r sst_ssd_bfp_risk_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_risk_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - ED + Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


#### Portion Size Trials

\FloatBarrier

```{r sst_ssd_bfp_risk_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_risk_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - PS + Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

## N-back

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(nback_balacc_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load + Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\FloatBarrier

```{r nback_balacc_bfp_risk_mod_posthoc, echo=FALSE}
emmeans(nback_balacc_bfp_risk_mod, specs = pairwise ~ risk_status_mom, adjust = 'none')
emmeans(nback_balacc_bfp_risk_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'none')
test(emtrends(nback_balacc_bfp_risk_mod, ~ bfp_center, var = 'bfp_center'))
```
\FloatBarrier

```{r nback_balacc_rwa_mod, echo=FALSE, results='asis'}
kable(nback_balacc_rwa$result, "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Relative Weighting Analysis', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\FloatBarrier

### d'

\FloatBarrier

```{r nback_dprime_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(nback_dprime_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback dprime - Body Fat Percentage x Load + Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\FloatBarrier
```{r nback_dprime_bfp_risk_mod_posthoc, echo=FALSE}
emmeans(nback_dprime_bfp_risk_mod, specs = pairwise ~ risk_status_mom, adjust = 'none')
emmeans(nback_dprime_bfp_risk_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'none')
test(emtrends(nback_dprime_bfp_risk_mod, ~ bfp_center, var = 'bfp_center'))
```
\FloatBarrier

```{r nback_dprime_rwa_mod, echo=FALSE, results='asis'}
kable(nback_dprime_rwa$result, "latex",  digits = 3, caption = 'Nback dprime - Relative Weighting Analysis', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

# Exploratory Analyses: remove BMI percentile >= 85 (reviewer comment)

## Go-NoGo

### Percent False Alarms

\FloatBarrier

```{r gng_fa_risk_p85_mod, echo=FALSE, results='asis'}
kable(round(gng_fa_risk_p85_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

### Percent Hits

```{r gng_hits_risk_p85_mod, echo=FALSE, results='asis'}
kable(round(gng_hits_risk_p85_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Percent Hits - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### Go Reaction Time

```{r gng_hits_rt_risk_p85_mod, echo=FALSE, results='asis'}
kable(round(gng_rt_risk_p85_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Go Reaction Time', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### d'

```{r gng_dprime_risk_p85_mod, echo=FALSE, results='asis'}
kable(round(gng_dprime_risk_p85_sum$coefficients, digits = 3), "latex",  digits = 3, caption = "Go-NoGo - d'", booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier
\clearpage

## Stop-Signal Task

### Stop Signal Reaction Time


#### Overall

\FloatBarrier

```{r sst_ssrt_risk_p85_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_risk_p85_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\

\FloatBarrier

### Stop Signal Delay

#### Overall

\FloatBarrier

```{r sst_ssd_risk_p85_mod, echo=FALSE, results='asis'}
kable(round(sst_ssd_risk_p85_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

\FloatBarrier
\clearpage

## N-back

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_risk_p85_mod, echo=FALSE, results='asis'}
kable(round(nback_balacc_risk_p85_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

### d'

\FloatBarrier

```{r nback_dprime_risk_p85_mod, echo=FALSE, results='asis'}
kable(round(nback_dprime_risk_p85_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

\clearpage

# Exploratory Analyses: adjust for BMI-Z score (reviewer comment)

## Go-NoGo

### Percent False Alarms

\FloatBarrier

```{r gng_fa_risk_bmiz_mod, echo=FALSE, results='asis'}
kable(round(gng_fa_risk_bmiz_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

### Percent Hits

```{r gng_hits_risk_bmiz_mod, echo=FALSE, results='asis'}
kable(round(gng_hits_risk_bmiz_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Percent Hits - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### Go Reaction Time

```{r gng_hits_rt_risk_bmiz_mod, echo=FALSE, results='asis'}
kable(round(gng_rt_risk_bmiz_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Go Reaction Time', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### d'

```{r gng_dprime_risk_bmiz_mod, echo=FALSE, results='asis'}
kable(round(gng_dprime_risk_bmiz_sum$coefficients, digits = 3), "latex",  digits = 3, caption = "Go-NoGo - d'", booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier
\clearpage

## Stop-Signal Task

### Stop Signal Reaction Time


#### Overall

\FloatBarrier

```{r sst_ssrt_risk_bmiz_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_risk_bmiz_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\

\FloatBarrier

### Stop Signal Delay

#### Overall

\FloatBarrier

```{r sst_ssd_risk_bmiz_mod, echo=FALSE, results='asis'}
kable(round(sst_ssd_risk_bmiz_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

\FloatBarrier
\clearpage

## N-back

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_risk_bmiz_mod, echo=FALSE, results='asis'}
kable(round(nback_balacc_risk_bmiz_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

### d'

\FloatBarrier

```{r nback_dprime_risk_bmiz_mod, echo=FALSE, results='asis'}
kable(round(nback_dprime_risk_bmiz_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

\clearpage
